---
title: "Daniel Vartanian's CV"
author: Daniel Vartanian
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ["resume", "css/dd_cv.css", "css/custom.css"]
    self_contained: true
---

<!-- See <https://pagedown.rbind.io/#resume> to learn more. -->

```{r load-packages, include=FALSE}
library(beepr)
library(checkmate)
library(cli)
library(datadrivencv)
library(dplyr)
library(glue)
library(googlesheets4)
library(here)
library(knitr)
library(lubridate)
library(magrittr)
library(metathis)
library(pagedown)
library(purrr)
library(rmarkdown)
library(stringr)
library(tibble)
library(tidyr)
library(withr)
```

```{r set-chunk-options, include=FALSE}
opts_chunk$set(
  results = "asis",
  echo = FALSE
)
```

```{r load-scripts, include=FALSE}
here("R", "get_data.R") |> source()
here("R", "tidy_data.R") |> source()
here("R", "print_data.R") |> source()
```

```{r set-metadata, echo=FALSE, message=FALSE, warning=FALSE}
meta() |>
  meta_name("github-repo" = "danielvartan/cv-research") |>
  meta_social(
    title = "Daniel Vartanian's CV",
    url = "https://danielvartan.github.io/cv-research",
    og_type = "website",
    og_author = "Daniel Vartanian",
    og_locale = "en_US.UTF-8"
  )
```

<!-- styles: start -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- styles: end -->

<!-- scripts: start -->
<script src="https://kit.fontawesome.com/ddcb976bc4.js" crossorigin="anonymous"></script>
<!-- scripts: end -->

```{r process-data, include = FALSE}
ss <- paste0(
  "https://docs.google.com/spreadsheets/d/",
  "1Cp-ebP86AXGIIpuGiFnTpquweFzMsH9M8QDIUQfZQEU"
)
```

```{r, include=FALSE}
data <-
  ss |>
  get_data() |>
  tidy_data()
```

# Aside

![Daniel Vartanian](https://avatars.githubusercontent.com/u/29462472?v=4){width=100% style='border-radius: 50%; text-align: center;'}

```{r render-cv-aside-1}
if (isTRUE(params$pdf_mode)) {
  cat(
    "<p style='font-size: 0.65rem; text-align: center;'>",
    "Access this CV online at: ",
    "[danielvartan.github.io/cv-research]",
    "(https://danielvartan.github.io/cv-research)",
    "</p>",
    sep = ""
  )
} else {
  cat(
    "<p style='text-align: center;'>",
    "[<i class = 'fas fa-download'></i>&nbsp; Download this CV]",
    "(pdf/Daniel%20Vartanian.pdf)",
    "</p>",
    sep = ""
  )
}
```

::: {style="text-align: left; padding-top:20px;"}
<h2 style="padding-bottom: 5px;">Contact</h2>

```{r}
data |> print_data("contact")
```

<h2 style="padding-top: 15px; padding-bottom: 15px;">References</h2>

```{r}
data |> print_data("references")
```
:::

## Disclaimer {#disclaimer}

Developed with [R](https://www.r-project.org)<br>[pagedown](https://github.com/rstudio/pagedown) and [datadrivencv](https://github.com/nstrayer/datadrivencv) packages.

Source code available at:<br>[github.com/danielvartan/cv-research](https://github.com/danielvartan/cv-research)

Last updated on `r with_locale(c("LC_TIME" = "en_US.UTF-8"), format(Sys.Date(), "%B %e, %Y"))`.

# Main

## Daniel Vartanian {#title}

::: {style="font-size: 0.7rem;"}
```{r render-cv-introduction}
data |> print_data("introduction")
```

:::
<!-- Positron bug -->

## Research Experience {#research data-icon=laptop}

```{r render-cv-research-experience}
data |> print_data("research_experience")
```

::: {.aside style="top: 0px;"}
<h2>Programming Languages</h2>

<p style="margin-top: 5px"><i class="fa-brands fa-github"></i>&nbsp;&nbsp; [danielvartan](https://github.com/danielvartan)</p>

```{r render-cv-aside-3}
data |> print_data("programming_languages")
```

:::
<!-- Positron bug -->

## Education {#education data-icon=graduation-cap}

```{r render-cv-education}
data |> print_data("education")
```

## Teaching Experience {#teaching data-icon=chalkboard-user}

```{r render-cv-teaching-experience}
data |> print_data("teaching_experience")
```

::: {.aside style="top: 0px;"}
<h2>Affiliations</h2>

```{r render-cv-aside-2}
data |> print_data("affiliations")
```

<h2 style="padding-top: 15px;">Languages</h2>

<p style="margin-top: 5px"><i class="fa-solid fa-crow"></i>&nbsp;&nbsp; [danielvartan](https://www.duolingo.com/profile/danielvartan)</p>

```{r}
data |> print_data("languages")
```

:::
<!-- Positron bug -->

## Selected Publications {#publications data-icon=book}

```{r render-cv-publications}
data |> print_data("publications")
```

## Selected Software Projects {#software data-icon=box-open}

```{r render-cv-software-development}
data |> print_data("software_development")
```

## Selected Outreach Projects {#outreach data-icon=users}

```{r render-cv-outreach}
data |> print_data("outreach")
```
